Hyper-linked Communications: WebRTC enabled asynchronous collaboration

### 2016-06-18 tese2/12_related_work_summary.tex
[RFT] last thesis commit?

In order to implement an hyper-linked communication solution, several design decisions had to be made. The limitations imposed by the \emph{Internet's} structure, its protocols and browser's capabilities are key factors to consider when implementing a solution that allows bi-directional communications, interactive media and collaboration environment.

>>>>

In order to implement an hyper-linked communication solution, several design decisions had to be made. The limitations imposed by the \emph{Internet's} structure, its protocols and browser's capabilities are key factors to consider when implementing a solution that allows bi-directional communications, interactive media and a collaboration environment.

### 2016-06-18 tese2/abstract.tex
[FIX] front cover typo
[RFT] last thesis commit?

Voice and image together can express emotions like no other medium can. With hypermedia concepts, we can add more value to conference calls.

\emph{WebRTC} technology allows real-time communications between web browsers without the need to install additional software. The nature of web browser applications already follows the hypermedia concept, which makes \emph{WebRTC} the ideal technology to apply the hyper-linked communications concepts.
The web browser platform provides an abstraction layer that makes it possible to create applications that run independently from the operating system.
The native support for \emph{WebRTC} in operating systems extends its usage to outside the web browser, allowing for the exploration of functionalities for which web browsers provide poor support, such as video recording and massive information storage.

%\sout{Our goal in this project is to develop an application that leverages the Hyper-linked communications concept to enable collaborative real-time audio and video communication, enriched with other media types, that can be accessed live or accessed later.}
%This application will target the web browser platform, resorting to \ac{WebRTC}.

Our goal was the development of an application targeted to the web platform, resorting to \emph{WebRTC}, that leveraged the hyper-linked communications by providing a conference environment enriched with multiple media types, collaborative text editors, time annotations, instant messaging, ability to superimpose hyper-content to video and the possibility to playback communications.

>>>>

%Voice and image together can express emotions like no other medium can. With hypermedia concepts, we can add more value to conference calls.

\emph{WebRTC} technology allows real time communications between web browsers without the need to install additional software. The nature of web browser applications already follows the hypermedia concept, which makes \emph{WebRTC} the ideal technology to apply the hyper-linked communications concepts.
The web browser platform provides an abstraction layer that makes it possible to create applications that run independently from the operating system.
The native support for \emph{WebRTC} in operating systems extends its usage to outside the web browser, allowing for the exploration of functionalities for which web browsers provide poor support, such as video recording and massive information storage.

%\sout{Our goal in this project is to develop an application that leverages the Hyper-linked communications concept to enable collaborative real time audio and video communication, enriched with other media types, that can be accessed live or accessed later.}
%This application will target the web browser platform, resorting to \ac{WebRTC}.

Our goal was the development of an application targeted to the web platform, resorting to \emph{WebRTC}, that leveraged the hyper-linked communications by providing a multi-party conference environment enriched with multiple media types, collaborative text editors, time annotations, instant messaging, ability to superimpose hyper-content to video and the possibility to playback communications.

### 2016-06-18 tese2/architecture.tex
[RFT] last thesis commit?

\begin{itemize}
 \item \textbf{Instant Messaging} - Our application must provide a simple way to send instant text messages to the conference participants.
 \item \textbf{Room management} - Conference rooms can be public or private. Public chat rooms are moderated by a group of clients which initially consists only of the room creator. This type of room has no access restrictions by default, but that can be changed by its moderators. Private chat rooms will only be visible to a defined list of clients or can be accessed by clients that have a link for that conference room.
 \item \textbf{Stream Recording} - Ability to record and playback recorded video including all the hyper-content displayed at that time.
 \item \textbf{Stream Composition} - Our streaming server must support mixing multiple user streams into a single stream. The sound played on clients must be the composed sound of all participants but the video played can be switched to the individual or group view.
 \item \textbf{Time annotations} - Our application must give the possibility to create annotations associated to a specified time and support viewing them on a timeline. 
 \item \textbf{Content Overlay} - Our system must allow users to superimpose hyper-content to video given a range of time. This content can be continuous or discrete and interactive or non interactive.
 \item \textbf{Search} - Unified search every objects related to a conference room such as hyper-content, time annotations and users.
 \item \textbf{Content Sharing} - Our application must have the ability to share files and time links among users.
 \item \textbf{Active talker detection} - The system must enable sound detection for showing the current speaker.
 \item \textbf{Collaboration} - The web application must provide a collaborative text edition tool.
 \item \textbf{QR Code detection} - The system must interpret \ac{QR} codes in order to ease content creation.
 \item \textbf{NAT Traversal} - The system's services must be available to users that are inside a private network.
 \item \textbf{Fault tolerance} - Our system's must use a database that supports data replication.
 \item \textbf{Scalability} - Our system must be horizontally scalable, which means that load must be distributed across web, streaming and database servers.
\end{itemize}

%RP capacidade de lidar com NAT

@@

 \item \textbf{Stream module} - responsible to deliver and receive multimedia content from the \emph{Client} using \ac{WebRTC}.

@@

\section{Implementation Proposal}
The infrastructure is composed by: web server, stream server, signaling server, database and video repository.
%RP tens da fazer o paralelo entre isto e os componentes apresentados na secção anterior. O mesmo com a imagem, que parece não estar relacionada. Podes colocar os elementos na mesma posição, ou dentro das caixas da imagem 3.1

@@

To qualify the above we provide public access to \ac{HTTP} server ports, maintaining the access to other components restricted through firewall rules.
%RP qualify?
%RP Imagem com firewall e estes portos? Mas isto já me parece muito detalhe de implementação.
In relation to the database there is no directly access from the outside. All the database information is accessed via our application server which validates the permissions of users on our system.

On the other hand, the access to our streaming servers is also restricted, but clients can connect to them after concluding the signaling phase. This signaling phase may or not proceed in function of the client access permissions. For example, if a user is trying to access a private conference room that he is not a member of nor has an invitation link for, the signaling server refuses to start the signaling phase and the user cannot access the streaming server.

@@

@@

	The composition of streams on client side is performed by receiving streams with the best quality possible but, due to undersizing the video of clients into a smaller region, this would result on wasting bandwidth on a quality that is not needed.

@@

>>>>

\begin{itemize}
 \item \textbf{Instant Messaging} - Our application must provide a simple way to send instant text messages to the conference participants.
 \item \textbf{Room management} - Conference rooms can be public or private. Public chat rooms are moderated by a group of clients which initially consists only of the room creator. This type of room has no access restrictions by default, but that can be changed by its moderators. Private chat rooms will only be visible to a defined list of clients or can be accessed by clients that have a link for that conference room.
 \item \textbf{Stream Recording} - Ability to record and playback recorded video including all the hyper-content displayed at that time.
 \item \textbf{Stream Composition} - Our streaming server must support mixing multiple user streams into a single stream. The sound played on clients must be the composed sound of all participants but the video played can be switched to the individual or group view.
 \item \textbf{Time annotations} - Our application must give the possibility to create annotations associated to a specified time and support viewing them on a timeline. 
 \item \textbf{Content Overlay} - Our system must allow users to superimpose hyper-content to video given a range of time. This content can be continuous or discrete and interactive or non interactive.
 \item \textbf{Search} - Search every objects related to a conference room such as hyper-content, time annotations and users.
 \item \textbf{Content Sharing} - Our application must have the ability to share files and time links among users.
 \item \textbf{Active talker detection} - The system must enable sound detection for showing the current speaker.
 \item \textbf{Collaboration} - The web application must provide a collaborative text edition tool.
 \item \textbf{QR Code detection} - The system must interpret \ac{QR} codes in order to ease content creation.
 \item \textbf{NAT Traversal} - The system's services must be available to users that are inside a private network.
 \item \textbf{Fault tolerance} - Our system's must use a database that supports data replication.
 \item \textbf{Scalability} - Our system must be horizontally scalable, which means that load must be distributed across web, streaming and database servers.
\end{itemize}

%RP capacidade de lidar com NAT
% HR-FINAL - Collaboration VS QRCode, completamente diferentes
% HR-FINAL - annotation vs content, specified time VS range of time, timeline VS superimposed video content (what else?)

@@

 \item \textbf{Stream module} - responsible to receive and deliver multimedia content to the \emph{Client} using \ac{WebRTC}.

@@

\section{Implementation Proposal}
The infrastructure is composed by: web server, stream server, database and video repository.
%RP tens da fazer o paralelo entre isto e os componentes apresentados na secção anterior. O mesmo com a imagem, que parece não estar relacionada. Podes colocar os elementos na mesma posição, ou dentro das caixas da imagem 3.1

% HR-FINAL - Corrigido

@@

To qualify the above we provide public access to \ac{HTTP} server ports, maintaining the access to other components restricted through firewall rules.
%RP qualify?
%RP Imagem com firewall e estes portos? Mas isto já me parece muito detalhe de implementação.
In relation to the database there is no direct access from the outside. All the database information is accessed via our application server which validates the permissions of users on our system.

On the other hand, the access to our streaming servers is also restricted, but clients can connect to them after concluding the signaling phase. This signaling phase may or not proceed in function of the client's access permissions. For example, if a user is trying to access a private conference room that he is not a member of nor has an invitation link for, the signaling server refuses to start the signaling phase and the user cannot access the streaming server.

% HR-FINAL - Bastava o cliente saber o a API do KMS, ligar-se a ele e controla-lo como se fosse administrador (o servidor web faz isso). Uma forma de ter o servidor publico e ano ser vulneravel a ameaças passaria por configurar a firewall de forma a bloquear o acesso indevido.

@@

% HR-FINAL - KMS? Não só, também as ligações por websocket são centralizadas, por isso é que não especifiquei na figura se era KMS ou WebServer.

@@

% HR-FINAL - Já foi definido. Sim é o que está escrito.

	The composition of streams on client side could be performed by receiving streams with the best quality possible from other users but, due to resizing the video of clients into a smaller region, this would result on wasting bandwidth on a quality that is not needed.

% HR-FINAL - is VS could = could wins. Receive video with the best quality from other users... resizing

@@

% HR-FINAL - "all conference participants are connected to the same server" sim é mesmo isso, se não fosse teria que enviar as mensagens entre varios servidores (é o que está escrito)

### 2016-06-18 tese2/introduction.tex
[RFT] last thesis commit?

	As communications technologies appeared, we adapted the way we communicate. The purpose of this project is not the replacement of the current video and audio communications, but to enrich them with hyper-media content and make them a more natural and easy to learn process.

@@

	For multiple reasons, we often need to repeat or postpone some of our tasks, some people tend to forget what they hear or see.

	Therefore, a real time system is a huge source of information that requires much attention from its users. In this context, an application that provides a way to remember our past communications would be a strong tool for not only to catch what we lost but also to enhance our knowledge.

@@

	In addition to this conference environment, which provides different functionalities than traditional conference environments such as \emph{Skype} and \emph{Google Hangouts}, we also enable a collaborative text editor and a chat that supports sending time hyper-links (to navigate to a location in time) and files to conference participants.

@@

@@

Making it clear, this project aims to complement current audio, text and video communications in order to create rich and collaborative interfaces with the ability to add more content on a future time (\emph{e.g.} creating time annotations for improving content search) in order to increase its value. It is also important to highlight another goal of this project which is the ability to navigate in time by rewinding communications, fast-forward and jump to certain points.

>>>>

	As communications technologies appeared, we adapted the way we communicate. The purpose of this project is not the replacement of the current video and audio communications, but to enrich them with hyper-media content. 
%HR-FINAL - corrigido

@@

%	For multiple reasons, we often need to repeat or postpone some of our tasks, some people tend to forget what they hear or see.

	A real time system is a huge source of information that requires much attention from its users. In this context, an application that provides a way to remember our past communications would be a strong tool for not only to catch what we lost but also to enhance our knowledge.

@@

% HR-FINAL - Não mencionei??? ("possibility to playback communications" VS "ability to navigate in time in order to reproduce the conversation ")

	In addition to this conference environment, which provides different functionalities than traditional conference environments such as \emph{Skype} and \emph{Google Hangouts}, we also enable a collaborative text editor and a chat that support sending time hyper-links (to navigate to a location in time) and files to conference participants.

@@

% HR-FINAL - Coloquei multi-party no abstract, não tenho muita margem para ecrever mais

@@

Making it clear, this project aims to complement current audio, text and video communications in order to create rich and collaborative interfaces with the ability to add more content on a future time (\emph{e.g.} creating time annotations for improving content search) in order to increase its value. It is also important to highlight another goal of this project, which is the ability to navigate in time by rewinding communications, fast-forward and jump to certain points.

### 2016-06-18 tese2/resumo.tex
[RFT] last thesis commit?

A voz e a imagem justas exprimem emoções como nenhum outro tipo de media permite. Através dos conceitos de hiper-media, podemos adicionar mais valor às comunicações por vídeo-conferência.

@@

O nosso objectivo neste projecto é desenvolver de uma aplicação, recorrendo ao \ac{WebRTC}, que utiliza o conceito de comunicações hiper-ligadas de forma a enriquecer as comunicações em conferência com vários tipos de media, editores de texto colaborativos, anotações temporais, envio de mensagens, possilidade de sobrepor contéudo ao vídeo e voltar atrás no tempo.

>>>>

%A voz e a imagem justas exprimem emoções como nenhum outro tipo de media permite. Através dos conceitos de hiper-media, podemos adicionar mais valor às comunicações por vídeo-conferência.

@@

O nosso objectivo neste projecto é desenvolver uma aplicação, recorrendo ao \ac{WebRTC}, que utiliza o conceito de comunicações hiper-ligadas de forma a enriquecer as comunicações em conferência com vários tipos de media, editores colaborativos, anotações temporais, envio de mensagens, possilidade de sobrepor contéudo ao vídeo e voltar atrás no tempo.
